Proposed Solution

### 2017-01-22 CAV17/secs/arch.tex
add section on post analysis

\para{Rule refinement.}
\ennan{It seems so far I do not know how exactly this part works. 
Maybe we can write through this part after finish the 
section 6.}

>>>>

\para{Post Analysis.}
Finally, the intermediate representation generated by the learner is
analyzed to further refine the rules. One natural transformation
presented in the paper is to interpret generated (option, relation, option)
rules as the edges of a graph. We analyze the properties of this graph to
construct an ordering of rules by their importance in the system being
configured, as well as to produce a measure of complexity for any configuration
of the target system. Note that particular metrics developed in this paper are
not exhaustive. We believe the information contained in the intermediate
representation, unavailable to previous neural-network based techniques,
to contain vast potential for further inquiry.
